---
title: "Rprofiling"
author: "Isaac Tetteh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rprofiling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The Rprofiling package consists of Five function. All these function takes one argument, which is of a class dataframe. Below are the functions:

* dsetinfo to give information on variables, observation, missig values and uniqness of the data

* var_types gives a count of the data type of the variables

* sample_data give a sample of the data

* data_summary usese the **summary** function to summerise the data.

* vis_mdata visualises the missig data in the dataset.

* full_profile combine all the above functon into one



```{r}
library(tidyverse)
library(Amelia)
```

### Examples on how to use dsetinfo(data) function
```{r, echo=TRUE}
Rprofiling::dsetinfo(mtcars)
```

### Examples on how to use var_types(data) function
```{r, echo=FALSE}
Rprofiling::var_types(mtcars)
```

### Examples on how to use sample_data(data) function
```{r, echo=FALSE}
Rprofiling::sample_data(mtcars)
```

### Examples on how to use data_summary(data) function
```{r, echo=FALSE}
Rprofiling::data_summary(mtcars)
```

### Examples on how to use vis_mdata(data) function
```{r, fig.show='hold'}
Rprofiling::vis_mdata(mtcars)
```
### Examples on how to use full_profile(data) function
```{r, echo=FALSE}
Rprofiling::full_profile(mtcars)
```
